---
title: "Final Homework"
author: "Erin Anderson"
date: "`r Sys.Date()`"
output: html_document
  theme: cerulean
  highlight: tango

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Challenges: 
 
# I had a hard time using the strsplit() command and still am having trouble calling characters out of my character vector. By using ?strsplit() I was able to obtain some help with the command and better understand the ways in which to best apply it.

# I also had a lot of trouble with working directories and making my working directory a place that is unique to my current repo. Through arduous trial and error and an embarrassing number of YouTube videos I was able to identify my problem and now hold a better understanding for file saving and re-accessing repos.

# Finally, I struggled with changing df to logical and factor values, and still could use some help with that code.

## CHALLENGE 1
```{r challenge 1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

v1<-("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
strsplit(v1, split = " ", fixed = FALSE, perl = FALSE, useBytes = FALSE)
v1[seq(from = 1, to = 22, by = 3)]

```
# I created the character vector v1 to comprise of the given text. I think used the strsplit() function to split each character within the string. Finally I sequenced my characters by 3.

## CHALLENGE 2
```{r challenge 2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
a<-m[, 2]
b<-m[,3]
c<-m[,6]
x<-c(a, b, c)
```
# I assigned each column to a variable, "a", "b", or "c" and then assigned x as a character vector comprising of a, b, and c
```{r challenge 2.2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
d<-m[6,]
e<-m[8,]
x<-c(d, e)
```
# I used the same method as before to assign rows to individual characters, and then used a character vector to assign both rows to variable x.
```{r challenge 2.3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
g<-m[2,2]
h<-m[6,9]
x<-c(g:h)
```

# I used the same method as before, but this time included : to signify I was including all characters from m[2,2] up to and including m[6,9]

## CHALLENGE 3
```{r challenge 3, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

a <- array(data = 1:400, dim = c(5, 5, 4, 4))
a[1, 1, 1, 2]
#[1] 101
a[2, 3, 2, ]
#[1]  37 137 237 337
a[1:5, 1:5, 3, 3]
# [,1] [,2] [,3] [,4] [,5]
# [1,]  251  256  261  266  271
# [2,]  252  257  262  267  272
# [3,]  253  258  263  268  273
# [4,]  254  259  264  269  274
# [5,]  255  260  265  270  275
```
# Here I created the array and used brackets to call different data and rows out.

## CHALLENGE 4
```{r challenge 4, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Tarsioidea <- c("Tarsiidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Tarsioidea, Catarrhini, Platyrrhini)
names(Anthropoidea) <- list("Tarsioidea", "Catarrhini", "Platyrrhini")
Haplorhini <- list(Anthropoidea)
names(Haplorhini) <- list("Anthropoidea")
Primates <- c("Haplorini", "Strepsirhini")
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
```

# Challenge 4 was my favorite. I feel like nesting characters within lists was easy to understand. I copied the same method for every nest, first assigning catergories with their families, and then nesting the assigned catergories into overarching orders.

## CHALLENGE 5
```{r challenge 5, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
m3 <- matrix(data = "3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2", nrow = 5, ncol = 3, byrow = FALSE)
data <- data.frame(m3)
data [, 2] <- as.logical(data[, 2])
data [, 3] <- as.factor(data[, 3])
```
# I made a matrix "m3" and then coerced it into a data frame. From there I made the second column logical valued and the third column factor valued.