---
title: "HomeworkEdits"
author: "Erin Anderson"
date: "`r Sys.Date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Challenges: I had a hard time using the strsplit() command and still am having trouble calling characters out of my character vector.

I also had a lot of trouble with working direcotries and making my working directory a place that is unique to my current repo.

Finally, I struggled with changing df to logical and factor values, and still could use some help with that code.

## CHALLENGE 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

v1<-("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
v1 <- strsplit(v1, split = " ")
v1[seq(from = 1, to = 22, by = 3)]

```
## I created the character vector v1 to comprise of the given text. I think used the strsplit() function to split each character within the string. Finally I sequenced my characters by 3.

## CHALLENGE 2
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
a<-m[, 2]
b<-m[,3]
c<-m[,6]
x<-c(a, b, c)
```
## I assigned each column to a variable, "a", "b", or "c" and then assigned x as a character vector comprising of a, b, and c
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
d<-m[6,]
e<-m[8,]
x<-c(d, e)
```
## I used the same method as before to assign rows to individual characters, and then used a character vector to assign both rows to variable x.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
g<-m[2,2]
h<-m[6,9]
x<-c(g:h)
```

## I used the same method as before, but this time included : to signify I was including all characters from m[2,2] up to and including m[6,9]

## CHALLENGE 3
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

a <- array(data = 1:400, dim = c(5, 5, 4, 4))
a[1, 1, 1, 2]
#[1] 101
a[2, 3, 2, ]
#[1]  37 137 237 337
a[1:5, 1:5, 3, 3]
# [,1] [,2] [,3] [,4] [,5]
# [1,]  251  256  261  266  271
# [2,]  252  257  262  267  272
# [3,]  253  258  263  268  273
# [4,]  254  259  264  269  274
# [5,]  255  260  265  270  275
```
## Here I created the array and used brackets to call different data and rows out.

## CHALLENGE 4
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Tarsioidea <- c("Tarsiidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Tarsioidea, Catarrhini, Platyrrhini)
names(Anthropoidea) <- list("Tarsioidea", "Catarrhini", "Platyrrhini")
Haplorhini <- list(Anthropoidea)
names(Haplorhini) <- list("Anthropoidea")
Primates <- c("Haplorini", "Strepsirhini")
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Strepsirhini")
```
m3 <- matrix(data = "3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2", nrow = 5, ncol = 3, byrow = FALSE)
#5x3 matrix row wise
df <- m3
#Made matrix into a data frame
is.logical(df[,2])
#makes the column logical
is.factor(df[,3])
#makes column factor-valued